Document knowledge base linking for information retrieval

### 2016-02-12 paper.tex
revisions

\documentclass{sig-alternate}
\usepackage{verbatim}
\usepackage{array}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage[table]{xcolor}
\usepackage{xcolor,colortbl}
\usepackage{enumitem}
\usepackage{multirow}
\usepackage{tabularx}

@@

\maketitle
\begin{abstract}
Entity linking and wikification are the tasks of matching mentions of an entity, such as a person, place, or organization, or a concept with its representation in a knowledge base such as Wikipedia. While there has been some investigation into use of entity linking in information retrieval, its usage may be hampered by the computational expense of constructing accurate entity annotations on large corpora, the frequent need for training data to construct entity links, and the ambiguity involved in real-world entity linking. We present a method by which a ``bag of links'' from a document to a knowledge base may be generated using standard information retrieval techniques with Wikipedia. We also suggest a document expansion approach that employs these links, which is effective in improving retrieval results.
\end{abstract}

@@

Entity linking and wikification have been the subject of much research, especially from the Text Analysis Conference (TAC) Knowledge Base Population (KBP) entity linking track. Systems are designed to link mentions of entities or concepts found in the text to their representations in a knowledge base such as Wikipedia\footnote{http://wikipedia.org} or Freebase\footnote{http://freebase.org}.

@@

In this paper, we present a method of using standard information retrieval techniques to produce a ``bag of links'' for each document in a corpus. To demonstrate their utility, we employ our knowledge base links using a simple document expansion model, which yields improvement over IR baselines.

@@

In contrast, our approach is concerned with \textit{document} expansion. It is based on two-stage smoothing \cite{Zhai2004}; however, while two-stage smoothing generally uses the collection as its background language model, we introduce the knowledge base description text. Our idea is closely related to Wei and Croft's LDA-based document model, which smooths the document language model with latent Dirichlet allocation probabilities \cite{Wei2006}. Liu and Croft's \textit{CBDM} model performs a similar type of smoothing by interoplating the probability of a query term in a document cluster with its probability in the document \cite{Liu2004}.

@@

We assume that a query is generated by a mixture of the document model $\theta_D$ and a model $\theta_K$ representing the concepts linked from the knowledge base. We assume that $\theta_K$ can be estimated using the linked knowledge base concepts $\mathcal{E}_D$. This mixture model may be expressed as:
%
\begin{flalign}\label{eq.ql-and-entities}
	\hat{P}^\lambda(Q|D) &= \prod_{i=1}^m (1-\lambda) P(q_i|D) + \lambda P(q_i|\mathcal{E}_D)
\end{flalign}

@@

\begin{table}[htbp]
\centering
\begin{tabular}{|c|p{0.28\textwidth}|c|} \hline
{\bf Param} & {\bf Meaning} & {\bf Value} \\ \hline
$k$ & The maximum number of document terms to use in constructing $D_Q$. & 20 \\ \hline
$n$ & The maximum number of knowledge base entries in $\mathcal{E}_D$. & 10 \\ \hline
$\lambda$ & Mixing parameter controlling the weights of $P(q|D)$ and $P(q|E)$ & 0.0-1.0 \\ \hline
$\mu$ & Used for Dirichlet smoothing of both $P(q|D)$ and $P(q|E)$. & 2500 \\ \hline
%$fbDocs$ & The number of feedback documents to use for RM3 runs. & 20 \\ \hline
%$fbTerms$ & The number of terms per document to use for RM3 runs. & 20 \\ \hline
%$\alpha$ & Mixing parameter controlling the weights of the original query and relevance model for RM3 runs. & 0.5 \\ \hline
\end{tabular}
\caption{Parameter settings for the entity linking procedure and retrieval model}
\label{table.parameters}
\end{table}

@@

\begin{table}[htbp]
\centering
\begin{tabular}{|c|l|c|c|} \hline
& {\bf Run} & {\bf $\lambda$} & {\bf MAP} \\ \hline
\multirow{3}{*}{Robust} & {\it baseline-ql} & -- & 0.2183 \\ \cline{2-4}
& {\it kb-ql} & 0.9 & {\bf 0.2275} \\ \cline{2-4}
& {\it stanbol-ql} & 0.1 & 0.1928 \\ \hline \hline 
\multirow{3}{*}{AP} & {\it baseline-ql} & -- & 0.2346 \\ \cline{2-4}
& {\it kb-ql} & 0.9 & {\bf 0.2515} \\ \cline{2-4}
& {\it stanbol-ql} & 0.1 & 0.1951 \\ \hline
\end{tabular}
\caption{The top-scoring runs and baselines by MAP. Bolded values indicate statistically significant improvements.}
\label{table.performance}
\end{table}

@@

Retrieval performance of the baselines and top-scoring runs are shown in Table \ref{table.performance}. Bolded mean average precision (MAP) scores are greater than the baseline run with statistical significance at $p < 0.001$ using a paired t-test. Note that baselines correspond to $\lambda = 0.0$.

Though Table \ref{table.performance} shows only the top-scoring values of $\lambda$, performance for \textit{kb} runs improved over the baseline for all values of $0.0 < \lambda < 1.0$, as shown in Figure \ref{figure.sweeps-ql}(a). All improvements were statistically significant with at least $p < 0.05$. We may explain the sudden drop in MAP at $\lambda=1.0$ by imagining a scenario in which two documents link to the same set of entities though only one of the documents is a good match for the query. The loss of this direct document-query score may be the cause of the drop at $\lambda=1.0$ since, in this case, documents are scored only using their linked entities. Further investigation is needed on this subject.

>>>>

\documentclass{sig-alternate}
\usepackage{verbatim}
\usepackage{array}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage[table]{xcolor}
\usepackage{xcolor,colortbl}
\usepackage{enumitem}
\usepackage{multirow}
\usepackage{tabularx}

@@

\maketitle
\begin{abstract}
Entity linking and wikification are the tasks of matching mentions of an entity, such as a person, place, or organization, or a concept with its representation in a knowledge base such as Wikipedia. While there has been some investigation into use of entity linking in information retrieval, its usage may be hampered by the computational expense of constructing accurate entity annotations on large corpora, the frequent need for training data to construct entity links, and the ambiguity involved in real-world entity linking. We present a method by which a ``bag of links'' from a document to a knowledge base may be generated using standard information retrieval techniques with Wikipedia. We also suggest a document expansion model that employs these links, which is effective in improving retrieval results.
\end{abstract}

@@

Entity linking and wikification have been the subject of much research, spurred recently by the Text Analysis Conference (TAC) Knowledge Base Population (KBP) entity linking track. Systems are designed to link mentions of entities or concepts found in the text to their representations in a knowledge base such as Wikipedia\footnote{http://wikipedia.org} or Freebase\footnote{http://freebase.org}.

@@

In this paper, we present a document expansion retrieval model to incorporate a ``bag of links'' into the document retrieval task. This model is in contrast to prior work applying entity links to IR, which has focused on \textit{query} expansion. Our document expansion model yields improvement over IR baselines.

@@

In contrast, our approach is concerned with \textit{document} expansion. This expansion entails linearly interpolating the document language model with a second model estimated from the knowledge base links, discussed further in Section \ref{section.model}. Our idea is closely related to Wei and Croft's LDA-based document model, which smooths the document language model with latent Dirichlet allocation probabilities \cite{Wei2006}. Liu and Croft's \textit{CBDM} model performs a similar type of document expansion by interpolating the probability of a query term in a document cluster with its probability in the document \cite{Liu2004}.

@@

We assume that a query is generated by a mixture of the document model $\theta_D$ and a model $\theta_K$ representing the concepts linked from the knowledge base. We assume that $\theta_K$ can be estimated using the linked knowledge base concepts $\mathcal{E}_D$. This mixture model may be expressed as:
%
\begin{flalign}\label{eq.ql-and-entities}
	\hat{P}^\lambda(Q|D) &= \prod_{i=1}^{|Q|} (1-\lambda) P(q_i|D) + \lambda P(q_i|\mathcal{E}_D)
\end{flalign}

@@

\begin{table}[htbp]
\centering
\begin{tabular}{|c|p{0.28\textwidth}|c|} \hline
{\bf Param} & {\bf Meaning} & {\bf Value} \\ \hline
$k$ & The maximum number of document terms to use in constructing $Q_D$. & 20 \\ \hline
$n$ & The maximum number of knowledge base entries in $\mathcal{E}_D$. & 10 \\ \hline
$\lambda$ & Mixing parameter controlling the weights of $P(q|D)$ and $P(q|E)$ & 0.0-1.0 \\ \hline
$\mu$ & Used for Dirichlet smoothing of both $P(q|D)$ and $P(q|E)$. & 2500 \\ \hline
%$fbDocs$ & The number of feedback documents to use for RM3 runs. & 20 \\ \hline
%$fbTerms$ & The number of terms per document to use for RM3 runs. & 20 \\ \hline
%$\alpha$ & Mixing parameter controlling the weights of the original query and relevance model for RM3 runs. & 0.5 \\ \hline
\end{tabular}
\caption{Parameter settings for the entity linking procedure and retrieval model}
\label{table.parameters}
\end{table}

@@

\begin{table}[htbp]
\centering
\begin{tabular}{|c|l|c|c|} \hline
& {\bf Run} & {\bf $\lambda$} & {\bf MAP} \\ \hline
\rule{0pt}{2.5ex} \multirow{3}{*}{Robust} & {\it baseline-ql} & -- & 0.2183 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it kb-ql} & 0.9 & 0.2275$^{\uparrow}$ \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it stanbol-ql} & 0.1 & 0.1928$^{\downarrow}$ \\ \hline \hline 
\rule{0pt}{2.5ex} \multirow{3}{*}{AP} & {\it baseline-ql} & -- & 0.2346 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it kb-ql} & 0.9 & 0.2515$^{\uparrow}$ \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it stanbol-ql} & 0.1 & 0.1951$^{\downarrow}$ \\ \hline
\end{tabular}
\caption{The top-scoring runs and baselines by MAP. Values marked with $\uparrow$ are statistically significant improvements over baselines, while values marked with $\downarrow$ are statistically significant declines.}
\label{table.performance}
\end{table}

@@

Retrieval performance of the baselines and top-scoring runs are shown in Table \ref{table.performance}. Mean average precision (MAP) scores marked with $\uparrow$ are greater than the baseline run with statistical significance at $p < 0.001$ using a paired t-test; those marked with $\downarrow$ show statistically significant declines at the same $p$-value. Note that baselines correspond to $\lambda = 0.0$.

Though Table \ref{table.performance} shows only the top-scoring values of $\lambda$, performance for \textit{kb} runs improved over the baseline for all values of $0.0 < \lambda < 1.0$, as shown in Figure \ref{figure.sweeps-ql}(a). All improvements were statistically significant with at least $p < 0.05$. We may explain the sudden drop in MAP at $\lambda=1.0$ by imagining a scenario in which two documents link to the same set of entities while only one of the documents is a good match for the query. The loss of this direct document-query score may be the cause of the drop at $\lambda=1.0$ since, in this case, documents are scored only using their linked entities. Further investigation is needed on this subject.
